The E-C Algorithm: conceptual bootstrapping via grammar-based program compression.

### 2013-01-22 drafts/ijcai2013/ijcai13.tex
Added digitial arithmetic stuff.

In Figure~\ref{fig:symreg}, we show performance results as we vary
both the routers included and the frontier size. Each individual plot
shows how changing the frontier size changes the number of tasks the
algorithm identifies correctly over the course of ten algorithm
iterations. In addition, we have a baseline for each curve, visits the
same number of expressions as the corresponding algorithm run
(i.e. frontier size $\times$ $\#$ of iterations) but all at once; it
does not do any learning. Thus, this baseline serves as a brute-force
control for the learning aspect of the algorithm.

\begin{figure}

\includegraphics[width=\linewidth]{figures/learningCurves.pdf}
\includegraphics[width=\linewidth]{figures/performanceFrontierSize.pdf}
\caption{E-C learning curves for the symbolic regression task set as
  we vary the frontier size.}
\label{fig:symreg} 
\end{figure}

>>>>

In Figure~\ref{fig:symreg}, we show performance results as we vary the
frontier size. Each individual plot shows how changing the frontier
size changes the number of tasks the algorithm identifies correctly
over the course of fifteen algorithm iterations. In addition, we have a
baseline for each curve, visits the same number of expressions as the
corresponding algorithm run (i.e. frontier size $\times$ $\#$ of
iterations) but all at once; it does not do any learning. Thus, this
baseline serves as a brute-force control for the learning aspect of
the algorithm.

\begin{figure}
\begin{subfigure}[Before]{0.45\linewidth}
\includegraphics[width=\linewidth]{figures/learningCurves2.pdf}
\end{subfigure}
\begin{subfigure}[After]{0.45\linewidth}
\includegraphics[width=\linewidth]{figures/performanceVsFrontierSize2.pdf}
\end{subfigure}
\caption{E-C learning curves for the symbolic regression task set as
  we vary the frontier size.}
\label{fig:symreg} 
\end{figure}
